\plaintitle

### 2017-08-22 docs/papers/IoT2017/transactions.tex
updated the layout
no message

The previous subsection gave an overview of how PETRa uses
transactions in the trading workflow to transfer various assets.  We
now describe the format of these transactions, as well as the rules
that they have to satisfy to be valid and recorded on the ledger.  We
also introduce and detail regulatory transactions, which the DSO uses
to regulate the microgrid.

@@

\subsubsection{Energy and Financial Transactions}
Energy and financial transactions transfer energy and financial assets
from one address to another.  Prosumers can use these transactions for
multiple purposes, {\em e.g.}, to trade energy by exchanging assets
with other prosumers, to prove to the bid storage service that they
possess an asset, to hide their identity by transferring assets to and
from mixing services, and to deposit assets at their smart meter.
%
An energy and financial transaction contains the following fields:
\begin{itemize}[noitemsep,topsep=-\parskip]
\item \field{EPA\_in}: list of EPA inputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{out}: reference to an EPA output of a previous transaction,
\item \field{sig}: signature of the referenced output's address,
\end{itemize}
\item \field{ECA\_in}: list of ECA inputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{out}: reference to an ECA output of a previous transaction,
\item \field{sig}: signature of the referenced output's address,
\end{itemize}
\item \field{FA\_in}: list of FA inputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{out}: reference to an FA output of a previous transaction,
\item \field{sig}: signature of the referenced output's address,
\end{itemize}
\item \field{EPA\_out}: list of EPA outputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{EPA}: an energy production asset,
\item \field{address}: address to which EPA is transferred,
\end{itemize}
\item \field{ECA\_out}: list of ECA outputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{ECA}: an energy consumption asset,
\item \field{address}: address to which ECA is transferred,
\end{itemize}
\item \field{FA\_out}: list of FA outputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{FA}: a financial asset,
\item \field{address}: address to which FA is transferred.
\end{itemize}
\end{itemize}
\vspace{0.5\parskip} This transaction transfers the assets specified
in the input lists to the addresses specified in the output lists.
Input and output lists may differ in length, so one asset may be
divided into multiple assets, and multiple assets may be combined into
one.

An energy and financial transaction is valid (and can be recorded on
the ledger) if the following three conditions hold.
\begin{itemize}[noitemsep,topsep=-\parskip]
\item None of the outputs referenced by the inputs have been spent by
  a transaction that has been recorded on the ledger.
\item All signatures are valid, which ensures that an asset can be
  transferred only by its current owner. 
\item For each asset type (and for each timestep), the sums of the
input and output assets are equal.  For example, in the case of
energy production assets, the condition is
\begin{align*}
& \forall t: \sum_{\substack{out \,\in\, \field{EPA\_out}:\\out.\field{EPA}.\field{start} \leq t \leq out.\field{EPA}.\field{end}}} out.\field{EPA}.\field{power} \nonumber \\
& = \sum_{\substack{in \,\in\, \field{EPA\_in}:\\in.\field{out}.\field{EPA}.\field{start} \leq t \leq in.\field{out}.\field{EPA}.\field{end}}} in.\field{out}.\field{EPA}.\field{power}  .
\end{align*}
The conditions for consumption and financial assets can be described
formally in similar ways.
\end{itemize}

>>>>

The previous subsection gave an overview of how PETra uses
transactions in the trading workflow to transfer various assets.  We
now describe the format of these transactions, as well as the rules
that they have to satisfy to be valid and recorded on the ledger.  We
also introduce and detail regulatory transactions, which the DSO uses
to regulate the microgrid.

@@

\subsubsection{Energy and Financial Transactions}
Energy and financial transactions transfer energy and financial assets
from one address to another.  Prosumers can use these transactions for
multiple purposes, {\em e.g.}, to trade energy by exchanging assets
with other prosumers, to prove to the bid storage service that they
possess an asset, to hide their identity by transferring assets to and
from mixing services, and to deposit assets at their smart meter.
%
An energy and financial transaction contains the following fields:
\begin{itemize}[noitemsep,topsep=-\parskip]
\item \field{EPA\_in}: list of EPA inputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{out}: reference to an EPA output of a previous transaction,
\item \field{sig}: signature of the referenced output's address,
\end{itemize}
\item \field{ECA\_in}: list of ECA inputs (i.e., list of (\field{out}, \field{sig}) pairs), %, each of which is defined by
%\begin{itemize}[leftmargin=0.5em,nosep]
%\item \field{out}: reference to an ECA output of a previous transaction,
%\item \field{sig}: signature of the referenced output's address,
%\end{itemize}
\item \field{FA\_in}: list of FA inputs (i.e., list of (\field{out}, \field{sig}) pairs), %, each of which is defined by
%\begin{itemize}[leftmargin=0.5em,nosep]
%\item \field{out}: reference to an FA output of a previous transaction,
%\item \field{sig}: signature of the referenced output's address,
%\end{itemize}
\item \field{EPA\_out}: list of EPA outputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{EPA}: an energy production asset,
\item \field{address}: address to which EPA is transferred,
\end{itemize}
\item \field{ECA\_out}: list of ECA outputs (i.e., (\field{ECA}, \field{address}) pairs), %, each of which is defined by
%\begin{itemize}[leftmargin=0.5em,nosep]
%\item \field{ECA}: an energy consumption asset,
%\item \field{address}: address to which ECA is transferred,
%\end{itemize}
\item \field{FA\_out}: list of FA outputs (i.e., (\field{ECA}, \field{address}) pairs). %, each of which is defined by
%\begin{itemize}[leftmargin=0.5em,nosep]
%\item \field{FA}: a financial asset,
%\item \field{address}: address to which FA is transferred.
%\end{itemize}
\end{itemize}
\vspace{0.5\parskip} This transaction transfers the assets specified
in the input lists to the addresses specified in the output lists.
Input and output lists may differ in length, so one asset may be
divided into multiple assets, and multiple assets may be combined into
one.

An energy and financial transaction is valid (and can be recorded on
the ledger) if the following three conditions hold.
\begin{itemize}[noitemsep,topsep=-\parskip]
\item None of the outputs referenced by the inputs have been spent by
  a transaction that has been recorded on the ledger.
\item All signatures are valid, which ensures that an asset can be
  transferred only by its current owner. 
\item For each asset type (and for each timestep), the sums of the
input and output assets are equal.  For example, in the case of
energy production assets, the condition is
\begin{align*}
 \forall t: ~ & \textstyle \sum_{\substack{out ~ \in ~ \field{EPA\_out}:\\out.\field{EPA}.\field{start} \, \leq \, t \, \leq \, out.\field{EPA}.\field{end}}} out.\field{EPA}.\field{power} \nonumber \\
 & \textstyle = \sum_{\substack{in ~ \in ~ \field{EPA\_in}:\\in.\field{out}.\field{EPA}.\field{start} \, \leq \, t \, \leq \, in.\field{out}.\field{EPA}.\field{end}}} in.\field{out}.\field{EPA}.\field{power}  .
\end{align*}
The conditions for consumption and financial assets can be described
formally in similar ways.
\end{itemize}
